Strings functions analysis

### 2022-08-28 article.tex
all csharp functions added
all php functions added

@@

    \textbf{Ruby}: new, try\_convert, \%, *, +, +@, -@, <<, <=>, ==, ===, =\~, [], []=, ascii\_only?, b, bytes, bytesize, byteslice, capitalize, capitalize!, casecmp, casecmp?, center, chars, chomp, chomp!, chop, chop!, chr, clear, codepoints, concat, count, crypt, delete, delete!, delete\_prefix, delete\_prefix!, delete\_suffix, delete\_suffix!, downcase, downcase!, dump, each\_byte, each\_char, each\_codepoint, each\_grapheme\_cluster, each\_line, empty?, encode, encode!, encoding, end\_with?, eql?, force\_encoding, freeze, getbyte, grapheme\_clusters, gsub, gsub!, hash, hex, include?, index, initialize\_copy, insert, inspect, intern, length, lines, ljust, lstrip, lstrip!, match, match?, next, next!, oct, ord, partition, prepend, replace, reverse, reverse!, rindex, rjust, rpartition, rstrip, rstrip!, scan, scrub, scrub!, setbyte, size, slice, slice!, split, squeeze, squeeze!, start\_with?, strip, strip!, sub, sub!, succ, succ!, sum, swapcase, swapcase!, to\_c, to\_f, to\_i, to\_r, to\_s, to\_str, to\_sym, tr, tr!, tr\_s, tr\_s!, undump, unicode\_normalize, unicode\_normalize!, unicode\_normalized?, unpack, unpack1, upcase, upcase!, upto, valid\_encoding?.

    \textbf{C#}:

    \textbf{PHP}:

>>>>

    \textbf{Ruby}: new, try\_convert, \%, *, +, +@, -@, <<, <=>, ==, ===, =\~, [], []=, ascii\_only?, b, bytes, bytesize, byteslice, capitalize, capitalize!, casecmp, casecmp?, center, chars, chomp, chomp!, chop, chop!, chr, clear, codepoints, concat, count, crypt, delete, delete!, delete\_prefix, delete\_prefix!, delete\_suffix, delete\_suffix!, downcase, downcase!, dump, each\_byte, each\_char, each\_codepoint, \\ each\_grapheme\_cluster, each\_line, empty?, encode, encode!, encoding, end\_with?, eql?, force\_encoding, freeze, getbyte, grapheme\_clusters, gsub, gsub!, hash, hex, include?, index, initialize\_copy, insert, inspect, intern, length, lines, ljust, lstrip, lstrip!, match, match?, next, next!, oct, ord, partition, prepend, replace, reverse, reverse!, rindex, rjust, rpartition, rstrip, rstrip!, scan, scrub, scrub!, setbyte, size, slice, slice!, split, squeeze, squeeze!, start\_with?, strip, strip!, sub, sub!, succ, succ!, sum, swapcase, swapcase!, to\_c, to\_f, to\_i, to\_r, to\_s, to\_str, to\_sym, tr, tr!, tr\_s, tr\_s!, undump, unicode\_normalize, unicode\_normalize!, unicode\_normalized?, unpack, unpack1, upcase, upcase!, upto, valid\_encoding?.

    \textbf{C\#}:

    Clone, CompareTo, Contains, EndsWith, Equals, GetHashCode, GetType, GetTypeCode, IndexOf, ToLower, ToUpper, Insert, IsNormalized, LastIndexOf, Remove, Replace, Split, StartsWith, Substring, ToCharArray, Trim.

    \textbf{PHP}: addcslashes, addslashes, bin2hex, chop, chr, chunk\_split, convert\_cyr\_string, convert\_uudecode, convert\_uuencode, count\_chars, crc32, crypt, echo, explode, fprint, get\_html\_translation\_table, hebrev, hebrevc, hex2bin, html\_entity\_decode, htmlentities, htmlspecialchars\_decode, htmlspecialchars, implode, join, lcfirst, levenshtein, localeconv, ltrim, md5, md5\_file, metaphone, money\_format, nl\_langinfo, nl2br, number\_format, ord, parse\_str, print, printf, quoted\_printable\_decode, quoted\_printable\_encode, quotemeta, rtrim, setlocale, sha1, sha1\_file, similar\_text, soundex, sprintf, sscanf, str\_getcsv, str\_ireplace, str\_pad, str\_repeat, str\_replace, str\_rot13, str\_shuffle, str\_split, str\_word\_count, strcasecmp, strchr, strcmp, strcoll, strcspn, strip\_tags, stripcslashes, stripslashes, stripos, stristr, strlen, strnatcasecmp, strnatcmp, strncasecmp, strncmp, strpbrk, strpos, strrchr, strrev, strripos, strrpos, strspn, strstr, strtok, strtolower, strtoupper, strtr, substr, substr\_compare, substr\_count, substr\_replace, trim, ucfirst, ucwords, vfprintf, vprintf, vsprintf, wordwrap.

@@
